HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

In HMEANT there are no guidelines as to when to propagate and error. In HUME errors are localised as far as possible to where they occur, by the separation of atomic and structural nodes. This allows us to calculate more acurately the total score of the sentence.

>>>>

In HMEANT, there are no guidelines as to when to propagate and error. In HUME,
errors are localised as much as possible to where they occur, by the separation of atomic and structural nodes. This allows us to calculate more acurately the total score of the sentence.
